---
title: "Spatial Mapping Examples"
output: html_notebook
date: "22 Sept 2016""
---

"The Marshall Project has collected and analyzed four decades of FBI data “on the most serious violent crimes in 68 police jurisdictions.” The FBI data covers 1975 through 2014; the reporters “also obtained data directly from 61 local agencies for 2015 — a period for which the FBI has not yet released its numbers.” Between 2010 and 2015, violent crime increased most in Milwaukee (+11%) and declined most in Prince George’s County, Md. (-22%).""

Data was derived from GitHub: https://github.com/themarshallproject/city-crime


```{r}
library(readr)
library(dplyr)
ucr_crime <- read_csv("~/Downloads/city-crime-master/data/ucr_crime_1975_2015.csv")
head(ucr_crime)
```

```{r}
dat2 <- tidyr::separate(ucr_crime, department_name, c("city", "state"), sep = ",")
head(dat2)
unique(dat2$city)
```


```{r}
library(ggmap)                                   
cities <- unique(dat2$city)                          # Create a list of the unique cities
#loc <- geocode(cities, output = "latlon")            # derive lat/lon for each city from ggmap API

loc.dat <- cbind(cities, loc)
head(loc.dat)
colnames(loc.dat)[1] <- "city"

loc.dat <- dplyr::filter(loc.dat, cities!="National")
head(loc.dat)
```


```{r}
library(leaflet)

leaflet(data = loc.dat) %>% 
  addTiles() %>%
  addMarkers(~lon, ~lat, popup = ~as.character(city))
```


```{r}
#remerge the data
head(loc.dat)
head(dat2)

dat3 <- merge(dat2, loc.dat, by = "city", all.x = TRUE)
dat3  <- subset(dat3, dat2$year==2014)
qmplot(lon, lat, data = dat3, size = violent_crime)

```

```{r}
addCircleMarkers(
    radius = ~ifelse(type == "ship", 6, 10),
    color = ~pal(type),
    stroke = FALSE, fillOpacity = 0.5
  )

```
